### 2021-01-12 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
manuscript updated

\subsection*{Schema acquisition}
\label{schema_acq}
In the first step of our semantic reconciliation methodology, we collect medical schema from \textbf{three} distinct information systems. The include ....

>>>>

\subsection*{Schema acquisition}
\label{schema_acq}
In the first step of our semantic reconciliation methodology, we collect medical schema from five distinct EMR storage systems. These include patient reports from OpenEMR ($m_1$), 100,000 patient records from EMRBOTS ($m_2$) \cite{kartoun2016methodology}, custom database design by Pan et. al($m_3$) for supporting regional clinics and health care centers in China \cite{pan2016design}, clinical knowledge discovery tool MedTAKMI-CDI ($m_4$) \cite{inokuchi2007medtakmi}, and our custom implementation ($m_5$).
In our earlier work \cite{Satti2020} $m_1$, $m_2$, and $m_3$ were used to generate over 115 million patient records, which are converted into a semi-structured form and stored in Hadoop Distributed File System (HDFS). We extended the same setup to \textbf{further include}
